What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
removing mistakes on paragraph wrapping

%\noindent\emph{3) Odd Wrappings}
\subsection{Odd Wrappings}
Table~\ref{wrappingandroid} presents the wrappings found in this study for all
stack traces found in Android repositories. As we can see, some of the checked
exceptions where indeed wrapped in runtime exceptions or even errors, while most
of them were not wrapped along the stack trace (represented as the table lines
on which the Wapper type is -).

>>>>

%\noindent\emph{3) Odd Wrappings}
\subsection{Odd Wrappings}
Table~\ref{wrappingandroid} presents the wrappings found in this study for all
stack traces found in Android repositories. As we can see, some of the checked
exceptions where indeed wrapped in runtime exceptions or even errors, while most
of them were not wrapped along the stack trace.
